\documentclass[margin]{res}
\textwidth=5.2in
\usepackage[hidelinks]{hyperref}

\newcommand*{\desicenteredline}[1]{%
    \ifhmode\expandafter\\\else\noindent\fi
    \hspace*{-\sectionwidth}%
    \hbox to \dimexpr\sectionwidth+\linewidth\relax{\hss #1\hss}\hskip0pt\relax}

\begin{document}

\desicenteredline{\Large\bf Yuji Shen}
\desicenteredline{\underline{\href{mailto:yuji.shen.work@gmail.com}{yuji.shen.work@gmail.com}}}

\address{{\bf SCHOOL ADDRESS} \\ 407 Jishi Bldg. \\ No.4800 Cao'an Highway \\
        Shanghai, 201804 \\
        (86) 13818633460 }
\address{{\bf PERMANENT ADDRESS} \\ Room 1005, No.32 \\ Lane 100, Zhongtan Rd. \\
        Shanghai, 200061 \\
        (86) 13818633460 }

\begin{resume}
\desicenteredline{\hrulefill}

\section{OBJECTIVE}
Microsoft - Software Developer Engineer Intern (Shanghai)

\section{EDUCATION}
Master of Engineering, {\bf Software Engineering} \\
Tongji University, Shanghai \hfill Sep. 2012 - Present \\
Average Score : 86 / 100

Bachelor of Engineering, {\bf Software Engineering} \\
Tongji University, Shanghai \hfill Sep. 2008 - Jun. 2012 \\
GPA : 4.2 / 5.0

\section{EXPERIENCE}
{\bf Software Engineering Intern} \\
QAD China R\&D Center, Shanghai \hfill Jul. 2011 - Mar. 2012
\begin{itemize}
\item Converted old PROGRESS reports to new .Net reporting framework. Wrote PROGRESS code at the server side and a little vb-script at the client side.
\item Helped analyzing the efficiency bottleneck of certain operations and helped improving the efficiency.
\item Created all the 'browsers' in the project named 'Serialization'. Solved several problems which had never been met.
\item Participated in a project which aimed to use perl script to find all the hardcoded data type in the whole system.
\end{itemize}

\section{PROJECT \\ EXAMPLES}
{\bf Restaurant Ordering System} \hfill Sep. 2012 - Dec. 2012 \\
Course Project of Object-Oriented Programming. This system aimed to introduce a mechanism of ordering in the restaurant by using Android Platform and Webservice.
\begin{itemize}
\item Did pre-coding investigation and helped team leader to decide the specific technologies to use.
\item Designed system outline behaviors and the interfaces of sub-systems.
\item Designed and implemented the Webservice side logic independently using Axis2 framework.
\item Designed and implemented Webservice API package for Android platform.
\end{itemize}
{\bf TJADRI CDPlugin} \hfill Jun. 2010 - Jun. 2011 \\
Cooperation project with the Architectural Design and Research Institute of Tongji University. The plugin helps the architects to manage the design steps with AutoCAD. The main Feature is the electronic sign and its verification. It was implemented with C\# and ObjectARX.
\begin{itemize}
\item Communicated with customers and helped them to decide their demands.
\item Discussed with another team member every week. Designed all the functions together according to our weekly discussions.
\item Implemented more than half functional demands, including the electronic sign and other assistant demands.
\end{itemize}

\section{SKILLS}
{\bf Programming Skills}
\begin{itemize}
\item C\textbackslash C++
\begin{itemize}
\item 4 years experience in school.
\item Wrote a text processing program on Windows console. (Course Project)
\item Wrote an Excel-liked sheet processing program using Windows Native API. (Course Project)
\end{itemize}
\item Java
\begin{itemize}
\item 3 years experience in school.
\item Wrote a restaurant ordering system based on Axis2 Webservice framework and Android platform. (Course Project)
\item Wrote a note application on Android platform. (Course Project)
\end{itemize}
\item Perl
\begin{itemize}
\item 1 year experience during the internship.
\item Wrote a code analyst analyzing script which helped the daily build framework to check code standard.
\item Wrote a code analyst analyzing script which go though the whole system to find hardcoded data type.
\end{itemize}
\end{itemize}
{\bf Non-Programming Skills}
\begin{itemize}
\item VIM
\end{itemize}

\section{SELF- \\ EVALUATION}
{\bf Communication Skills}
\begin{itemize}
\item Always keep communicating with members in the team and can play a positive role in team development.
\end{itemize}
{\bf Self-learning Skills}
\begin{itemize}
\item Willing and good at learning new techniques and knowledge. Can put new knowledge into practice in a short time.
\end{itemize}
{\bf English Document Reading}
\begin{itemize}
\item Used to reading English document, such as Stack Overflow and platform specific references.
\end{itemize}
{\bf Responsibility}
\begin{itemize}
\item Strong responsibility on own duties.
\end{itemize}
\end{resume}
\end{document}



